<!--
|  (C) 2006-2024 Potsdam Institute for Climate Impact Research (PIK)
|  authors, and contributors see CITATION.cff file. This file is part
|  of REMIND and licensed under AGPL-3.0-or-later. Under Section 7 of
|  AGPL-3.0, you are granted additional permissions described in the
|  REMIND License Exception, version 1.0 (see LICENSE file).
|  Contact: remind@pik-potsdam.de
-->
# Biomass Feedstock Differentiation Indicators 

## Price Bioenergy
```{r}
showLinePlots(data, "Prices|Bioenergy")
```

## Land Cover Bioenergy Crops
```{r}
showLinePlots(data, "Resources|Land Cover|Cropland|Croparea|Bioenergy crops")
```

## Demand 

### Demand - Bioenergy Total

```{r}
showLinePlots(data, "Demand|Bioenergy")
```

### Demand - Bioenergy 2nd gen

```{r}
showLinePlots(data, "Demand|Bioenergy|2nd generation")
```

### Demand - Bioenergy 1st gen
```{r}
showLinePlots(data, "Demand|Bioenergy|1st generation")
```

## REMIND Demand 

### PE Biomass Production
```{r PE Biomass Production}
items <- c(
  "PE|Production|Biomass|Lignocellulosic|Energy Crops",
  "PE|Production|Biomass|Lignocellulosic|Residues",
  "PE|Production|Biomass|1st Generation",
  NULL)
showAreaAndBarPlots(data, items, tot = "PE|Production|Biomass", orderVars = "user", scales = "fixed")
```

### PE Biomass Consumption
```{r PE Biomass}
tot <- "PE|Biomass"
items <- c(
  "PE|Biomass|Hydrogen|w/ CC",
  "PE|Biomass|Hydrogen|w/o CC",
  "PE|Biomass|Electricity|w/ CC",
  "PE|Biomass|Electricity|w/o CC",  
  "PE|Biomass|Heat",
  "PE|Biomass|Gases|w/ CC",
  "PE|Biomass|Gases|w/o CC",  
  "PE|Biomass|Liquids|w/ CC",
  "PE|Biomass|Liquids|w/o CC",
  "PE|Biomass|Solids",
  "PE|Biomass|Biochar",
  NULL)

showLinePlots(data, tot)
showAreaAndBarPlots(data, items, tot = tot, orderVars = "user", scales = "fixed")
```

## Productivity

### Productivity|Landuse Intensity Indicator Tau

```{r}
showLinePlots(data, "Productivity|Landuse Intensity Indicator Tau")
```

### Productivity|Crops

```{r}
showLinePlots(data, "Productivity|Yield|Crops")
```


### Productivity|Bioenergy Crops

```{r}
showLinePlots(data, "Productivity|Yield|Bioenergy crops")
```



## Land Cover 

### Resources|Land Cover Change

```{r}
items <- c(
  "Resources|Land Cover Change|Cropland",
  "Resources|Land Cover Change|Pastures and Rangelands",
  "Resources|Land Cover Change|Forest",
  "Resources|Land Cover Change|Other Land",
  "Resources|Land Cover Change|Urban Area")
showAreaAndBarPlots(data, items, scales = "fixed")
```

### Resources|Land Cover Change - LinePlots
```{r}
items <- c(
  "Resources|Land Cover Change|Cropland",
  "Resources|Land Cover Change|Pastures and Rangelands",
  "Resources|Land Cover Change|Forest",
  "Resources|Land Cover Change|Other Land",
  "Resources|Land Cover Change|Urban Area")
showMultiLinePlots(data, items, scales = "fixed")
```

### Crops for Food vs. Bioenergy Crops

```{r}
items <- c(
  "Resources|Land Cover|Cropland|Croparea|Bioenergy crops",
  "Resources|Land Cover|Cropland|Croparea|Crops",
  "Resources|Land Cover|Cropland|Croparea|Forage")
showAreaAndBarPlots(data, items, scales = "fixed")
```

### Crops for Food vs. Bioenergy Crops - LinePlots
```{r}
items <- c(
  "Resources|Land Cover|Cropland|Croparea|Bioenergy crops",
  "Resources|Land Cover|Cropland|Croparea|Crops",
  "Resources|Land Cover|Cropland|Croparea|Forage")
showMultiLinePlots(data, items, scales = "fixed" )
```

### Types of Bioenergy Crops

```{r}
items <- c(
  "Resources|Land Cover|Cropland|Croparea|Bioenergy crops|Short rotation grasses", 
  "Resources|Land Cover|Cropland|Croparea|Bioenergy crops|Short rotation trees"
  )
showAreaAndBarPlots(data, items, scales = "fixed")
```


# Other Indicators 
## Biodiversity

```{r results='asis'}
items <- c(
  "Biodiversity|BII",
  "Biodiversity|Biodiversity Hotspot BII",
  "Biodiversity|Cropland Landscapes BII",
  "Biodiversity|Key Biodiversity Area BII",
  "Biodiversity|BII in areas outside Biodiversity Hotspots, Intact Forest & Cropland Landscapes",
  "Biodiversity|Shannon crop area diversity index")
walk(items, function(v) {
  cat("###", v, "\n\n")
  showLinePlots(data, v, ylim = NULL, scales = "fixed")
  cat("\n\n")
})
```


